\chapter{Acknowledgement}

First of all, we would like to express our sincere gratitude and appreciation to our thesis advisor Assoc. Prof. Trần Minh Triết for the continuous support of our study and research. With his patience, conscientious guidance, enthusiast support, we have acquired valuable knowledge in the fields of Machine Learning, Deep Learning, Computer Vision. Our thesis could not completed without his friendly guidance and expert advice.

We also would like to say thanks to Prof. Minh N. Do from University of Illinois at Urbana-Champaign and Dr. Benjamin Chidester from Carnegie Mellon University for their extended discussions and valuable suggestions which have contributed greatly to the improvement of the thesis.

Moreover, we are grateful to all of our lecturers in the Faculty in Information and Technology, University of Science, VNUHCM. They have built us a solid foundation in Computer Science, especially in Artificial Intelligence field, which makes it easier for us to acquire deeper knowledge to finish our thesis.

Besides, we are really thankful for our generous colleagues at the SELAB, University of Science: Trương Thành Đạt, Bùi Ngọc Minh, Đỗ Trọng Lễ, Lương Quốc An, Trần Mai Khiêm who are always here to help us and give valuable comments whenever we need their support.   

Last but not least, our deepest gratitude goes to all of our parents. It would not be possible to write this thesis without their immeasurable support, caring and encouragement throughout our education. 

\begin{flushright}
\begin{minipage}{8cm}
\centering
Authors

Hoàng Trung Hiếu \& Tôn Thất Vĩnh 
\end{minipage}
\end{flushright}