\chapter{Thesis Proposal}
\begin{longtable}{|l|c|}
\hline
\multicolumn{2}{|m{\linewidth}|}{\textbf{Thesis title}: ENHANCING VIDEO SUMMARIZATION WITH CONTEXT AWARENESS
}\\
\hline
\multicolumn{2}{|m{\linewidth}|}{\textbf{Advisors}: Assoc.Prof. Trần Minh Triết, Dr. Lê Trung Nghĩa} \\
\hline
\multicolumn{2}{|m{\linewidth}|}{\textbf{Duration}: January 1\textsuperscript{st}, 2023 to August 14\textsuperscript{th}, 2023}\\
\hline
\multicolumn{2}{|m{\linewidth}|}{\textbf{Students}: Huỳnh Lâm Hải Đăng (19125003) - Hồ Thị Ngọc Phượng (19125014)}\\
\hline
\multicolumn{2}{|m{\linewidth}|}{\textbf{Theme of Thesis}: theoretical research, proposed improvements.}\\
\hline
\multicolumn{2}{|m{\linewidth}|}{\textbf{Content}:\par
We aim to propose a novel approach for improving video summarization quality by integrating context awareness. We also aim to propose an evaluation metric that better suits the practical use of problem in real life.\par
The details include:
\begin{itemize}
  \item Literature Review and Proposal Writing \begin{itemize}
    \item Conduct a comprehensive literature review on video summarization, identifying the current state-of-the-art techniques and their limitations, as well as opportunities for improvement. 
    \item Analyze the importance of context in video summarization and compare existing methods and tools for context extraction in videos, in terms of performance and applicability for video summarization.
    \item Develop a research proposal, including research questions, hypothesis, and methodology, based on the findings from the literature review.
  \end{itemize}
\end{itemize}}\\
\hline

\multicolumn{2}{|m{\linewidth}|}{\begin{itemize}
  \item Dataset Collection \begin{itemize}
    \item Collect datasets suitable for training and testing.
    \item Analyze the current evaluation metrics for video summarization and identify their flaws.
    \item Define relevant performance metrics for evaluating the effectiveness of the context awareness in improving the quality of video summarization.
  \end{itemize}
  \item Model Development\begin{itemize}
    \item Develop baseline model for the sake of benchmarking.
    \item Develop different models to prove the proposed hypothesis.
    \item Train and optimize the model using the collected datasets.
  \end{itemize}
  \item Comparison with Existing Video Summarization Techniques\begin{itemize}
    \item Conduct experiments on proposed enhancements with a thoroughly designed ablation study.
    \item Analyze the strengths and weaknesses of the proposed approach.
    \item Conduct surveys based on the proposed evaluation metric.
  \end{itemize}
  \item Demo Application Development\begin{itemize}
    \item Develop a demo application that can demonstrate the functionality and usability of the proposed framework for video summarization.
  \end{itemize}
\end{itemize}}\\
\hline

\multicolumn{2}{|m{\linewidth}|}{\begin{itemize}
  \item Thesis Writing and Submission\begin{itemize}
    \item Write up the thesis, including an introduction, literature review, methodology, results, discussion, and conclusion.
    \item Submit the thesis for review and evaluation by the thesis committee.
  \end{itemize}
\end{itemize}}\\

\multicolumn{2}{|m{\linewidth}|}{
\textbf{Implementation plan}:
\begin{itemize}
  \item Literature Review and Proposal Writing: 01-01-2023 to 31-01-2023
  \item Dataset Collection: 01-02-2023 to 15-02-2023
  \item Saliency Detection Model Development: 16-02-2023 to 15-03-2023
  \item Video Summarization Model Development: 16-03-2023 to 15-04-2023
  \item Integration of Saliency Detection into Video Summarization: 16-04-2023 to 15-05-2023
  \item Comparison with Existing Video Summarization Techniques: 16-05-2023 to 31-05-2023
  \item Demo Application Development: 01-06-2023 to 30-06-2023
  \item Thesis Writing and Submission: 01-07-2023 to 31-07-2023
\end{itemize}}\\
\hline
\makecell{\\ \textbf{Advisors} \vspace*{2cm} \\ Assoc. Prof. Trần Minh Triết \vspace*{2cm} \\ Dr. Lê Trung Nghĩa} & \makecell{\textbf{December 26\textsuperscript{th} 2022}\\ \textbf{Authors} \vspace*{2cm} \\ Huỳnh Lâm Hải Đăng \vspace*{2cm} \\ Hồ Thị Ngọc Phượng}\\
\hline
\end{longtable}

