\chapter{Acknowledgement}

% We would like to express our gratitude to Associate Professor Tran Minh Triet for his attentive guidance over the course of our undergraduate studies. He had sparked our interest in researching and contributing to science from our first courses, which enable us to continue working and complete this thesis.

% We would like to thank lecturers from Faculty of Information Technology, University of Science, VNU-HCM. From the first days, they had impressed us with their scholarly knowledge and wisdom, prompting us to learn more to further perfect ourselves.

% We would like to thank our friends who offered feedback and knowledge from many fields and topics. Thanks to them, we are able to learn many new aspects which help us construct our ideas.

% We would like to thank SELab, University of Science, VNU-HCM for the provided infrastructure. Thanks to the invaluable computing power, we were able to conduct the necessary experiments.

% Finally, we would like to thank our precious family for their unconditional love, support, and taking care of us through hard times. 


% eureka
We would like to express our gratitude to Associate Professor Tran Minh Triet for his attentive guidance over the course of our undergraduate studies. He had sparked our interest in researching and contributing to science from our first courses, which enable us to continue working and complete this project.

We would like to thank lecturers from Faculty of Information Technology, University of Science, VNU-HCM. From the first days, they had impressed us with their scholarly knowledge and wisdom, prompting us to learn more to further perfect ourselves.

We would like to thank our friends who offered feedback and knowledge from many fields and topics. Thanks to them, we are able to learn many new aspects which help us construct our ideas.

We would like to thank SELab, University of Science, VNU-HCM for the provided infrastructure. Thanks to the invaluable computing power, we were able to conduct the necessary experiments.

Finally, we would like to thank our precious family for their unconditional love, support, and taking care of us through hard times. 